### 2023-06-08 application.tex
up

\begin{theorem}{}
Resilience is decidable for continuous VASS when $\Safe$ and $\Bad$ are definable in the existential theory of
the rationals with addition and order.
\end{theorem}

@@

\begin{center}
\begin{tabular}{ | l | c | c | c | r |}
\hline   \Safe~\Bad 
		& $\uparrow$~ $\downarrow$~ 
		 & $\downarrow$~ $\uparrow$~

 \\ \hline
   RP  
   	& Decidable (Thm~\ref{down-up})  
   		 & ??

    \\ \hline
   BRP  
   &  Decidable (Thm~\ref{down-up}) 
   		 & Decidable  ?

    \\ \hline
      kRP  
      & Decidable (Thm~\ref{down-up}) 
      		& Decidable ?

       \\ \hline
   sRP  
   	& Decidable (Thm~\ref{post srp})
   		 & ??

    \\ \hline
   BsRP  
   &  Decidable (Thm~\ref{ref ozkan})
   		 & ??

    \\ \hline
      ksRP   
      & Decidable (Thm~\ref{ref ozkan})
      		& ??

       \\ \hline

>>>>

\begin{theorem}\label{RP VASS}
Resilience is decidable for continuous VASS when $\Safe$ and $\Bad$ are definable in the existential theory of
the rationals with addition and order.
\end{theorem}

@@

\begin{center}
\begin{tabular}{ | l | c | c | c | r |}
\hline   \Safe~\Bad 
		& $\uparrow$~ $\downarrow$~ 
		 & $\downarrow$~ $\uparrow$~ 
 \\ \hline
   RP  & Decidable (Thm~\ref{down-up})   & Decidable (Thm~\ref{RP VASS})
    \\ \hline
   BRP   &  Decidable (Thm~\ref{down-up})  & Decidable (Thm~\ref{brp VASS})
    \\ \hline
      kRP       & Decidable (Thm~\ref{down-up}) & Decidable (Thm~\ref{brp VASS})
       \\ \hline
   sRP    	& Decidable (Thm~\ref{post srp})	 & ??
    \\ \hline
   BsRP     &  Decidable (Thm~\ref{ref ozkan})	 & ?? 
    \\ \hline
      ksRP        & Decidable (Thm~\ref{ref ozkan}) & ?? 
       \\ \hline
